\thesistitle

### 2019-06-13 sections/research.tex
Trying to explain something

Building the ``clone grid'' consists of walking the AST in-order for each declaration and statement. For each declaration/statement found, we map the following relations:
\begin{itemize}
  \item The declaration/statement preceding it.
  \item The declaration/statement following.
  \item The last \textbf{preceding} declaration/statement with which it is cloned.
\end{itemize}
We do not create a seperate grid for each class file, so the statement/declaration preceding or following could be in a different file. While mapping these relations, we maintain a hashed map containing the last occurrence of each unique statement. This map is used to quickly find out whether a statement is cloned with another.

@@

As stated in the previous section, nodes in the grid link to \textit{preceding} cloned statement. This implies that the first node that is cloned does not have any clone relation, as there are no clones preceding it (only following it). Because of this, we start our clone detection process at the final location encountered while building the grid. For this node, we collect all nodes it is cloned with. Even though the final node only links to the preceding node it is cloned with, we can collect all clones. This is because the preceding clone also has a preceding clone (if applicable) and we can follow this trail to collect all clones of a single node. As an example, see figure \ref{}

\begin{figure}[H]
  \centering
  \includegraphics[width=1\columnwidth]{img/CodeGraph}
  \caption{Clone grid as built by CloneRefactor.}
  \label{fig:clonegrid}
\end{figure}

>>>>

Building the ``clone grid'' consists of walking the AST in-order for each declaration and statement. For each declaration/statement found, we map the following relations:
\begin{itemize}
  \item The declaration/statement preceding it.
  \item The declaration/statement following.
  \item The last \textbf{preceding} declaration/statement with which it is cloned.
\end{itemize}
We do not create a seperate grid for each class file, so the statement/declaration preceding or following could be in a different file. While mapping these relations, we maintain a hashed map containing the last occurrence of each unique statement. This map is used to quickly find out whether a statement is cloned with another. An example of such a grid is displayed in figure \ref{fig:clonegridsimple}.

\begin{figure}[H]
  \centering
  \includegraphics[width=1\columnwidth]{img/CodeGraph2}
  \caption{Clone grid as built by CloneRefactor.}
  \label{fig:clonegridsimple}
\end{figure}

@@

As stated in the previous section, nodes in the grid link to \textit{preceding} cloned statement. This implies that the first node that is cloned does not have any clone relation, as there are no clones preceding it (only following it). Because of this, we start our clone detection process at the final location encountered while building the grid. For this node, we collect all nodes it is cloned with. Even though the final node only links to the preceding node it is cloned with, we can collect all clones. This is because the preceding clone also has a preceding clone (if applicable) and we can follow this trail to collect all clones of a single node. As an example, see figure \ref{fig:clonegrid}.

\begin{figure}[H]
  \centering
  \includegraphics[width=1\columnwidth]{img/CodeGraph3}
  \caption{Clone grid with a clone class consisting of three clone instances marked.}
  \label{fig:clonegrid}
\end{figure}

Using the example shown in figure \ref{fig:clonegrid} we can explain how we detect clones. Suppose we are currently finding clones at the purple marked box. We then follow all ``duplicate'' relations until we have found all clones (the boxes marked in green). We now have a single statement clone class. Next, we move to the previous line. Here again, we collect all duplicates of this node. For each of these duplicates, we check whether the node following it is already in the clone class we collected in the previous iteration. In this case, only two of the
